---
title: "Hotel Reservations"
date: "2023-04-08"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[1.1] Import the Hotel Reservations data into a temporary dataset `hotel` 
*/

#steps

1.Open RStudio or any R environment you are using.
2.Set the working directory to the location where the "hotel_reservations.csv" file is saved. You can do this using the setwd() function. For example, if the file is saved in the "Documents" folder of your computer, you can set the working directory as follows:setwd("~/Documents")
3.Install the 'readr' package and load it into the Rworkspace
4.Load the "hotel_reservations.csv" file into R using the read.csv() function and store it in a temporary dataset called hotel. 

```{r, message=FALSE, warning=FALSE}
library(readr)
hotel <- read_csv("C:/Users/Admins/Pictures/Hotel+Reservations.csv")
```



/*
[1.2] Check the imported data. Show which variables contain the booking date, and their format.
*/

#The str function can be used to show  variables that contain the booking date, and their format.

```{r}

str(hotel)

```



/* 
[1.3] Create a new variable `arrival` that contains a SAS date made out of arrival_month, arrival_date, arrival_year and assign a permanent date format to the new variable
*/

```{r,message=FALSE, warning=FALSE}
library(lubridate)

# Combine arrival_month, arrival_date, and arrival_year into a new variable called arrival
hotel$arrival <- mdy(paste(hotel$arrival_month, hotel$arrival_date, hotel$arrival_year, sep = "/"))

# Format arrival as "MM/DD/YYYY" and convert it back to a date object with the same format
hotel$arrival <- as.Date(format(hotel$arrival, "%m/%d/%Y"), "%m/%d/%Y")

# Assign a permanent date format to the arrival variable (optional)
attr(hotel$arrival, "format") <- "%m/%d/%Y"

# Save the modified data frame to a new file (optional)
write.csv(hotel, "modified_data.csv", row.names = FALSE)

```


/* 
[1.4] To check your calculation, print arrival arrival_year arrival_month arrival_date for the first 10 rows of `hotel` dataset
*/

```{r}
head(hotel[, c("arrival", "arrival_year", "arrival_month", "arrival_date")], 10)
```



/* 
[1.5] Calculate the number of bookings for each quarter (e.g. 2017/3, 2017/4, ...) only for bookings where the booking status is "Not_Canceled" hint: apply a temporary date format to arrival so it's displayed as 2017/4 instead of 02OCT2017
	(any date format that generates quarters is fine) Show the number and percentage of bookings for each quarter.
*/

```{r}
library(lubridate)

# Create a new column called "quarter" containing the quarter of the year for each booking
hotel$quarter <- quarter(hotel$arrival)

# Filter the data to include only "Not_Canceled" bookings
hotel_nc <- hotel[hotel$booking_status == "Not_Canceled", ]

# Calculate the number of bookings for each quarter
bookings_by_quarter <- table(hotel_nc$quarter, hotel_nc$arrival_year)

# Apply a temporary date format to arrival for display purposes
hotel_nc$arrival_temp <- format(hotel_nc$arrival, format = "%Y/%q")

# Calculate the total number of not canceled bookings
total_bookings <- nrow(hotel_nc)

# Calculate the percentage of bookings for each quarter
perc_by_quarter <- prop.table(bookings_by_quarter) * 100

# Print the number and percentage of bookings for each quarter
cat(sprintf("%-9s %-13s %-10s %-10s\n", "Quarter", "Arrival Year", "Bookings", "Percentage"))
for (i in 1:nrow(bookings_by_quarter)) {
  cat(sprintf("%-9s %-13s %-10d %-10.2f\n",
              rownames(bookings_by_quarter)[i],
              colnames(bookings_by_quarter)[i],
              bookings_by_quarter[i],
              perc_by_quarter[i]))
}
cat(sprintf("\nTotal number of not canceled bookings: %d\n", total_bookings))


```


/* 
[1.6] Print rows where arrival is missing, see if there's a pattern
*/

```{r}
missing_arrival <- hotel[is.na(hotel$arrival), ]
print(missing_arrival)
```


/*
[1.7] Remove rows from `hotel` where arrival is missing then re-run the table from Q1.5 to confirm.
*/

```{r}
library(zoo)
hotel_clean <- hotel[!is.na(hotel$arrival), ]
hotel_clean$arrival_qtr <- as.yearqtr(hotel_clean$arrival, "%Y/%q")
table(hotel_clean$arrival_qtr, useNA = "always")

```

/* 
Make a results table showing the average price of each room typein order of frequencyalso showing minimum, median, and maximum 
*/

```{r}
library(dplyr)

# create summary table of room types and prices
room_prices <- hotel_clean %>%
  group_by(room_type_reserved) %>%
  summarize(num_bookings = n(),
            avg_price = mean(avg_price_per_room),
            min_price = min(avg_price_per_room),
            med_price = median(avg_price_per_room),
            max_price = max(avg_price_per_room)) %>%
  arrange(desc(num_bookings))

# print results table
print(room_prices)


```

/* 
[1.8] Room types 1 and 4 are the most common Rename them with a custom format
	Room_Type 1: Budget
	Room_Type 4: City View
	others	   : Other
Group the other room types together Apply the format permanently to the `hotel` dataset
*/

```{r}
# create custom format for room types
room_format <- function(x) {
  ifelse(x == 1, "Budget", 
         ifelse(x == 4, "City View", "Other"))
}

# rename room types and group other room types together
hotel_clean$room_type <- room_format(hotel_clean$room_type_reserved)

# apply custom format permanently to hotel_clean
attr(hotel_clean$room_type, "format") <- "character"

```


/* 
Calculate detailed statistics for Budget and City View rooms and find out what winsorising the most extreme 10% of values would do
*/

```{r}
library(DescTools)

# create separate datasets for Budget and City View rooms
budget <- hotel_clean[hotel_clean$room_type == "Budget", ]
city_view <- hotel_clean[hotel_clean$room_type == "City View", ]

# calculate detailed statistics for Budget and City View rooms
budget_stats <- summary(budget$avg_price_per_room)
city_view_stats <- summary(city_view$avg_price_per_room)

```

1. Define 4 macro variables: type_1_p05 type_1_p95 type_4_p05 type_4_p95

```{r}
# Extract data for Room Type 1
room_type_1 <- subset(hotel, room_type_reserved == "Budget")
type_1_p05 <- quantile(room_type_1$avg_price_per_room, 0.05)
type_1_p95 <- quantile(room_type_1$avg_price_per_room, 0.95)

# Extract data for Room Type 4
room_type_4 <- subset(hotel, room_type_reserved == "City View")
type_4_p05 <- quantile(room_type_4$avg_price_per_room, 0.05)
type_4_p95 <- quantile(room_type_4$avg_price_per_room, 0.95)

```

2. Set type_1_p05 and type_1_p95 to the 5% and 95% values for Room_Type 1 (Budget)

```{r}
# Extract data for Room Type 1
room_type_1 <- subset(hotel, room_type_reserved == "Budget")

# Calculate 5th and 95th percentiles for Room Type 1
type_1_p05 <- quantile(room_type_1$avg_price_per_room, 0.05)
type_1_p95 <- quantile(room_type_1$avg_price_per_room, 0.95)

# Set macro variables
assign("type_1_p05", type_1_p05)
assign("type_1_p95", type_1_p95)


```

3. Set type_4_p05 and type_4_p95 to the 5% and 95% values for Room_Type 4 (City View)

```{r}
# Extract data for Room Type 4
room_type_4 <- subset(hotel, room_type_reserved == "City View")

# Calculate 5th and 95th percentiles for Room Type 4
type_4_p05 <- quantile(room_type_4$avg_price_per_room, 0.05)
type_4_p95 <- quantile(room_type_4$avg_price_per_room, 0.95)

# Set macro variables
assign("type_4_p05", type_4_p05)
assign("type_4_p95", type_4_p95)

```

4. Using one DATA step:
4a. Make a new dataset `hotel_winsorized`

```{r}
library(dplyr)

hotel_winsorized <- hotel %>%
  mutate(winsorized_price = ifelse(room_type_reserved == "Budget",
                                   pmax(type_1_p05, pmin(avg_price_per_room, type_1_p95)),
                                   ifelse(room_type_reserved == "City View",
                                          pmax(type_4_p05, pmin(avg_price_per_room, type_4_p95)),
                                          avg_price_per_room))) %>%
  filter(winsorized_price >= type_1_p05 & winsorized_price <= type_1_p95 | 
           winsorized_price >= type_4_p05 & winsorized_price <= type_4_p95)

```

4b. Using one multiple conditional processing clause AND YOUR MACRO VARIABLES:
	For "Room_Type 1" rows, 
		if avg_price_per_room is below the p05 cutoff, set it to p05 for room type 1
		if avg_price_per_room is above the p95 cutoff, set it to p95 for room type 1
	For "Room_Type 4" rows,
		if avg_price_per_room is below the p05 cutoff, set it to p05 for room type 4
		if avg_price_per_room is above the p95 cutoff, set it to p95 for room type 4
		
```{r}
# set p05 and p95 cutoffs for each room type
type_1_p05 <- quantile(hotel_winsorized$avg_price_per_room[hotel_winsorized$room_type_reserved == "Budget"], probs = 0.05)
type_1_p95 <- quantile(hotel_winsorized$avg_price_per_room[hotel_winsorized$room_type_reserved == "Budget"], probs = 0.95)
type_4_p05 <- quantile(hotel_winsorized$avg_price_per_room[hotel_winsorized$room_type_reserved == "City View"], probs = 0.05)
type_4_p95 <- quantile(hotel_winsorized$avg_price_per_room[hotel_winsorized$room_type_reserved == "City View"], probs = 0.95)

# create a copy of the original dataset
hotel_winsorized_processed <- hotel_winsorized

# apply conditional processing using macro variables
hotel_winsorized_processed$avg_price_per_room[hotel_winsorized_processed$room_type_reserved == "Budget" & hotel_winsorized_processed$avg_price_per_room < type_1_p05] <- type_1_p05
hotel_winsorized_processed$avg_price_per_room[hotel_winsorized_processed$room_type_reserved == "Budget" & hotel_winsorized_processed$avg_price_per_room > type_1_p95] <- type_1_p95
hotel_winsorized_processed$avg_price_per_room[hotel_winsorized_processed$room_type_reserved == "City View" & hotel_winsorized_processed$avg_price_per_room < type_4_p05] <- type_4_p05
hotel_winsorized_processed$avg_price_per_room[hotel_winsorized_processed$room_type_reserved == "City View" & hotel_winsorized_processed$avg_price_per_room > type_4_p95] <- type_4_p95

```
		
4c. Only put rows into hotel_winsorized if they are for Budget or City View bookings
*/

```{r}
hotel_winsorized <- hotel_winsorized[hotel_winsorized$room_type_reserved %in% c("Budget", "City View"), ]

```


/*
Calculate the final price range after winsorizing Produce one result table with the minimum, mean, and maximum values of avg_price_per_room With one row for Budget and one row for City View Apply a temporary label to room_type_reserved so it looks nice
*/

```{r, message=FALSE, warning=FALSE}
# Create a label for room_type_reserved
hotel_winsorized$room_type_label <- ifelse(hotel_winsorized$room_type_reserved == 1, "Budget", 
                                           ifelse(hotel_winsorized$room_type_reserved == 4, "City View", "Other"))

# Calculate final price range after winsorizing
final_price_range <- hotel_winsorized %>%
  group_by(room_type_label) %>%
  summarise(
    Label = first(room_type_label),
    Min = min(avg_price_per_room),
    Mean = mean(avg_price_per_room),
    Max = max(avg_price_per_room),
    P05 = ifelse(room_type_label == "Budget", type_1_p05, type_4_p05),
    P95 = ifelse(room_type_label == "Budget", type_1_p95, type_4_p95)
  )
final_price_range <- hotel_winsorized %>%
  group_by(room_type_label) %>%
  summarise(
    Label = first(room_type_label),
    Min = min(avg_price_per_room),
    Mean = mean(avg_price_per_room),
    Max = max(avg_price_per_room)
  )

# Print the result table
final_price_range

```


