---
title: "Introduction to nhanesdata2 Analysis with R"
date: "2023-03-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

It is recommended to use R Markdown to submit both the answers to each question and the relevant code used as a single document. You may, however, write your answer in a Word document and submit your code separately as a script file. In either case, make sure that your code is appropriately annotated using comments throughout. Importantly, ensure that your
code can be run in its entirety using the Source (for scripts) or Knit (for markdowns) commands.

#Background

The paper by Smiley et al. (Nutrients, 2019) examines the relationship between sleep duration and metabolic syndrome (MetS) using the NHANES 2013/2014 nhanesdata2. The authors defined MetS using the criteria established by Lee, Gurka and DeBoer (Expert Rev. Cardiovasc. Ther, 2016), which takes into account racial and age-specific differences in populations, resulting in a
complex formula to determine a score. For this exercise, we will rely on a simpler criterion published in the joint scientific statement on metabolic syndrome (Alberti et al, 2009). The criteria for a positive incidence of MetS is when at
least 3 of the following 5 conditions are present: “1) elevated waist circumference (≥88 cm for women and ≥102 cm for men), 2) elevated triglycerides (≥150 mg/dL) or drug treatment for elevated triglycerides, 3) low HDL cholesterol (<40 mg/dL for men and <50 mg/dL for women) or drug treatment for low HDL cholesterol, 4) elevated blood pressure (systolic ≥130 mm Hg, or
diastolic ≥85 mm Hg, or both) or antihypertensive drug treatment for a history of hypertension, and 5) elevated fasting glucose (≥100 mg/dL) or drug treatment for elevated glucose.” (Moore et al., 2017; Preventing Chronic Disease). For our purposes, we will further simplify these criteria by ignoring the treatment specifications above and limit our analysis to the clinical measurements. Additionally, Smiley et al. describe exclusion criteria to remove potential outliers, which must be applied. Specifically, subjects who reported sleep durations greater than mean + 2SD (two standard deviations) were excluded. Moreover, we will limit our study sample to adults 20 years or older and exclude females between 20 and 44 years of age who had a positive pregnancy test or self-reported that they were pregnant at the time of exam (use variable RIDEXPRG in the demographics file). The variables in the MetS criteria described above may contain missing nhanesdata2. To remedy this issue, one may apply a simple imputation technique: if a nhanesdata2 point is missing, replace it with the mean value of the variable. The ifelse() function could be used here but there are other alternatives.

1. Use the 2017/2018 NHANES nhanesdata2 repository to obtain and merge the relevant nhanesdata2 files, apply the above indicated exclusion criteria, and impute missing nhanesdata2 appropriately. Report the sample size of your nhanesdata2. (10 points)

```{r}

library(tidyverse) # data management (tidyr, dplyr) and plots (ggplot2)
library(foreign) # reading xport files

# Import data from NHANES page
# For this analysis we need the following files:

# 1. Demographics - demo and weighting variables

# Create temporary file to catch web data
demofile = tempfile()

# download data into temporary file using URL; right-click on file name to get URL
# Since we created tempfile, we need to specify it as the destination file
# You can specify other destfile instead and it will save it to your working directory

download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DEMO_J.XPT", 
              destfile = demofile,
              mode = "wb") # use 'wb' to read as binary file

# Now read the xport data into an R data frame
demodf = read.xport(demofile)  # using foreign package (file must be binary format)


# 2. Mental health

mhfile = tempfile()

download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DPQ_J.XPT",
              destfile = mhfile,
              mode = 'wb')

mhdf = read.xport(mhfile)


# 3. Diabetes
diabfile = tempfile()

download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DIQ_J.XPT",
              destfile = diabfile,
              mode = "wb")
diabdf = read.xport(diabfile)

# Blood sugar
a1cfile = tempfile()

download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/GHB_J.XPT",
              destfile = a1cfile,
              mode = "wb")
a1cdf = read.xport(a1cfile)

# 4. Smoking
smokefile = tempfile()
download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/SMQ_J.XPT",
              destfile = smokefile,
              mode = "wb")
smokedf = read.xport(smokefile)

# 5. BMI
bmifile = tempfile()
download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/BMX_J.XPT",
              destfile = bmifile,
              mode = "wb")
bmidf = read.xport(bmifile)



###############
# Stepwise merging
#nhanesdata = inner_join(demodf, mhdf, by="SEQN")
#nhanesdata = inner_join(nhanesdata, diabdf, by="SEQN")
#nhanesdata = left_join(nhanesdata, smokedf, by="SEQN")
###############


# Merging using "piping" + additional data manipulation
nhanesdata2 = inner_join(demodf, mhdf, by="SEQN") %>% 
  left_join(diabdf, by="SEQN") %>%    # keep all common to demo and MH
  left_join(a1cdf, by="SEQN") %>%      
  left_join(smokedf, by="SEQN") %>% 
  left_join(bmidf, by='SEQN')



nhanesdata2 = nhanesdata2 %>%
  
  select(SEQN, 
         RIAGENDR, # gender
         RIDAGEYR, # age
         INDHHIN2, # household income
         starts_with("DPQ"),  # MH screener questions
         DIQ010,   # doctor diagnosed diabetes
         LBXGH,    # A1c lab data
         SMQ020,   # Smoked at least 100 cigarettes in life
         BMXBMI,
         
         #Survey design variables
         SDMVPSU,
         SDMVSTRA,
         WTMEC2YR) %>% 
  
  # Transform/modify variables
  mutate_at(c("RIAGENDR", "DIQ010", "SMQ020"),
            na_if, 7) %>%
  mutate_at(c("RIAGENDR", "DIQ010", "SMQ020"),
            na_if, 9) %>%
  mutate_at(vars(starts_with("DPQ")),
            na_if, 7) %>%
  mutate_at(vars(starts_with("DPQ")),
            na_if, 9) %>%

  
  ############################################################
  # Exercise: Household income uses 77 and 99 for "refused"
  # and "Don't know". Change these codes to NA is above.
  ############################################################

  # Transform individual variables
  # Depression scale total -> dichotomous variable
  # rowSums(c("col1", "col2"), na.rm = T)
  
  # rowwise can be used instead

  mutate(deptot = rowSums(select(., starts_with("DPQ")), na.rm = T)) %>%
  mutate(depressed = factor(deptot > 9, labels = c("Min/mild", "Mod/Severe"))) %>%

 
  # Diabetes (diagnosed): make into factor (1=yes, 2=no), make "Borderline" (3) as Yes (1)
  
  mutate(diabetes = replace(DIQ010, which(DIQ010==3), 1)) %>%
  mutate(diabetes = factor(diabetes, labels = c("Yes", "No"))) %>%
  
  #############################################################
  # ## Exercise: Diabetes (screened) - create binary variable
  # for whether A1c > 6%.##
  #############################################################

  # Smoking: change to factor
  mutate(SMQ020 = factor(SMQ020, labels = c("Yes", "No"))) %>%
  
  # Age: cut into tertiles, make factor and add labels
  mutate(age_cat = cut(RIDAGEYR, 
                       breaks = quantile(RIDAGEYR, probs = c(0, 1/3, 2/3, 1)), 
                       include.lowest = T, 
                       labels = c("18-39", "40-61", "62+"))) %>% #includes 80+
  
  # Collapse HH Income categories
  mutate(income = case_when(
    INDHHIN2 %in% c(1:4, 13) ~ "0-20K",
    INDHHIN2 %in% c(5:8, 12) ~ "20-55K",
    INDHHIN2 %in% c(9, 10, 14,15) ~ "55-100K+"
  )) %>%
  
  # Gender
  mutate(RIAGENDR = factor(RIAGENDR, 
                           labels = c('Male', 'Female'))) %>%

  ###########################################################
  # Exercise: Locate and merge the data set containing BMI
  # and convert it to a categorical variable with 4 levels.
  # The description of the levels can be found here:
  #  https://www.ncbi.nlm.nih.gov/books/NBK278991/table/diet-treatment-obes.table4clas/
  ###########################################################
  
  # filter based on inclusion criteria
  filter(!is.na(diabetes)) %>%
  
  
   # BMI variable
  mutate(bmi_cat = cut(BMXBMI,
                       breaks = c(14.2, 24.6, 29.69, 33.5, 86.2),
                       labels = c("14.2-24.6", "24.6-29.69", "29.69-33.5", "33.5-86.2"), 
                       include.lowest = T)) 

#%>%
  #filter(BMXBMI >= 24.6)

# Save to local drive
save(nhanesdata2, file="nhanesdata.RData")

# Report sample size
nrow(nhanesdata2)

```
2. Create the factor variable MetS based on the criteria above and label the levels as MetS+ and MetS- corresponding to whether subjects have met or have not met the benchmark, respectively. (5 points)

```{r}
# Create a vector of 0s with length equal to the number of rows in the data
MetS <- rep(0, nrow(nhanesdata2))

# Assign 1 to each row where the subject meets the criteria for Metabolic Syndrome
MetS[nhanesdata2$waist_circumference >= 102 & nhanesdata2$triglycerides >= 150 & nhanesdata2$HDL_cholesterol < 40 &
       nhanesdata2$blood_pressure_systolic >= 130 | nhanesdata2$blood_pressure_diastolic >= 85 | nhanesdata2$use_of_medications == 1] <- 1
# Convert the MetS variable to a factor variable with levels "MetS-" and "MetS+"
MetS <- factor(MetS, levels = c(0, 1), labels = c("MetS-", "MetS+"))

```

3. Convert the variables RIAGENDR (sex), DMDEDUC2 (education), RIDRETH3 (race/ethnicity), and DMDMARTZ (marital status) into factor variables such that the levels and corresponding labels match those in Table 1 of the Smiley paper. (5 points)

```{r}
# Convert RIAGENDR to factor variable
nhanesdata2$RIAGENDR <- factor(nhanesdata2$RIAGENDR,
                          levels = c(1, 2),
                          labels = c("Male", "Female"))

# Convert DMDEDUC2 to factor variable
nhanesdata2$DMDEDUC2 <- factor(nhanesdata2$DMDEDUC2,
                          levels = c(1, 2, 3, 4, 5),
                          labels = c("<9th grade", "9-11th grade", "High school", "Some college/AA", "College graduate"))

# Convert RIDRETH3 to factor variable
nhanesdata2$RIDRETH3 <- factor(nhanesdata2$RIDRETH3,
                          levels = c(1, 2, 3, 4, 5, 6),
                          labels = c("Mexican American", "Other Hispanic", "Non-Hispanic White", "Non-Hispanic Black", "Other Race Including Multi-Racial", "Asian"))

# Convert DMDMARTZ to factor variable
nhanesdata2$DMDMARTZ <- factor(nhanesdata2$DMDMARTZ,
                          levels = c(1, 2, 3, 4, 5, 6, 77),
                          labels = c("Married", "Widowed", "Divorced", "Separated", "Never married", "Living with partner", "Refused"))

```

