---
title: "MS3253 - Operations Analytics LAB 5"
date: "3/9/2023"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Name : Lam Ho Ching

Student ID : 55517919

Question 1 - Unicorns


The "unicorns" data frame contains information about a few unicorn startups from https://www.cbinsights.com/research-unicorn-companies


```{r, message=FALSE, warning=FALSE}
library(tidyverse)
unicorns = tribble(
	~company, ~valuation_b, ~country,
	"Toutiao", "$75", "China",
	"Uber", "$72", "United States",
	"Didi Chuxing", "$56", "China",
	"WeWork", "$47", "United States",
	"GrabTaxi", "11", "Singapore"
)
unicorns
```


[Q1A] Change the data type of the "valuation_b" column so that it is a numeric/double column.

```{r}
unicorns$valuation_b <- as.numeric(gsub("[^[:digit:].]", "", unicorns$valuation_b))
unicorns
```

[Q1B] Change the country value "United States" to "USA".

```{r}
unicorns$country[unicorns$country == "United States"] <- "USA"
unicorns
```

Question 2 - Tony's Students

Dr. Tony Stark graduated with a PhD from MIT, and is now an assistant professor at City University of Hong Kong.  Suppose that you are a university administrator, and you wish to determine which students have taken courses taught by Tony Stark.

The data that you need is spread across multiple data tables:

Table 1: All CityU students


```{r}
students = tribble(
	~student_id, ~student_name,
	1, "Adam",
	2, "Brian",
	3, "Cherry",
	4, "Diana"
)
students
```


Table 2: All courses taken by CityU students

```{r}
students_courses = tribble(
	~semester, ~course_code, ~student_id,
	"2017/18 A", "CB2201", 1,
	"2017/18 A", "CB2201", 2,
	"2017/18 B", "CB2201", 3,
	"2017/18 B", "CB2201", 4,
	"2017/18 B", "MS3253", 1,
	"2017/18 B", "MS3253", 4
)
students_courses
```

Table 3: All CityU lecturers

```{r}
lecturers = tribble(
	~staff_id, ~staff_name,
	123, "Tony Stark",
	789, "James Rhodes"
)
lecturers
```


Table 4: All courses taught by CityU lecturers

```{r}
lecturers_courses = tribble(
	~semester, ~course_code, ~staff_id,
	"2017/18 A", "CB2201", 123,
	"2017/18 B", "CB2201", 789,
	"2017/18 B", "MS3253", 123
)
lecturers_courses
```

[Q2A] By matching the staff name, filter the "lecturers" data frame so that it contains the row for Dr. Tony Stark.Store the result in the variable "ts".

```{r}
library(dplyr)

# Filter the lecturers data frame to contain the row for Tony Stark
ts <- lecturers %>% filter(staff_name == "Tony Stark")
ts

```


[Q2B] Store the courses taught by Dr. Tony Stark into the variable "tsc". 

```{r}
# Select the courses taught by Dr. Tony Stark
ts_id <- filter(lecturers, staff_name == "Tony Stark")$staff_id
tsc <- filter(lecturers_courses, staff_id == ts_id) %>%
  select(semester, course_code, staff_id) %>%
  mutate(staff_name = "Tony Stark")
tsc

```


[Q2C] Store the students who took courses taught by Dr. Tony Stark into the variable "tssid".

```{r}
library(dplyr)

tssid <- students_courses %>%
  inner_join(lecturers_courses, by = c("semester", "course_code")) %>%
  inner_join(students, by = "student_id") %>%
  inner_join(lecturers, by = "staff_id") %>%
  filter(staff_name == "Tony Stark")
tssid
```


[Q2D] Compute the names and student IDs of the students who were taught by Dr. Tony Stark, and store the result into the variable `tss`.

```{r}
library(dplyr)

tss <- students_courses %>%
  inner_join(lecturers_courses, by = c("semester", "course_code")) %>%
  inner_join(students, by = "student_id") %>%
  inner_join(lecturers, by = "staff_id") %>%
  filter(staff_name == "Tony Stark") %>%
  select(student_id, student_name) %>%
  distinct()
tss
```


