---
title: "Pipeline data Analysis"
date: "2023-06-04"
output:
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,message=FALSE, warning=FALSE}

#Import the data
library(readr)
data <- read_csv("Pipeline data.csv")

#Data cleaning

# Find columns with only NA values
na_columns <- colSums(is.na(data)) == nrow(data)

# Remove columns with only NA values
data <- data[, !na_columns]

```

# Descriptive statistics 

```{r}

# Select relevant columns for analysis (excluding dates)
relevant_columns <- c("Business Unit", "Zip Code", "State", "Project Type", "Project Type (Detail)",
                      "Pursuit", "In-Process", "In-Process & Anchor Open", "Complete",
                      "Total Project Costs...13", "Allocation Check")

# Subset the data
subset_data <- data[, relevant_columns]

# Calculate summary statistics
summary(subset_data)

#Describe the data
library(psych)
describe(subset_data)

# View the first few rows of the data
head(subset_data)

```
# Exploratory Data Analysis

```{r,message=FALSE, warning=FALSE}
# Load required libraries
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)

# Explore the relationship between project type and completion status
completion_status <- data %>%
  group_by(`Project Type`, Complete) %>%
  summarize(count = n())
completion_status

# Count of projects by project type
project_type_counts <- data %>%
  group_by(`Project Type`) %>%
  summarize(count = n())


# Correlation matrix for numeric variables
numeric_cols <- select_if(data, is.numeric)
cor_matrix <- cor(numeric_cols)
print(cor_matrix)

# Visualization

# Count the number of projects by project type
project_type_counts <- data %>% count(`Project Type`, sort = TRUE)

# Bar plot of project type counts
ggplot(project_type_counts, aes(x = `Project Type`, y = n)) +
  geom_bar(stat = "identity", fill = "cornflowerblue") +
  labs(title = "Project Type Counts", x = "Project Type", y = "Count") +
  theme_bw()

# Reshape the data to long format
data_long <- tidyr::pivot_longer(data, cols = c(`Complete`, `In-Process`, `In-Process & Anchor Open`), names_to = "Status", values_to = "Count")


# Create a bar plot of completions, in-process, and in-process & anchor open by states
ggplot(data_long, aes(x = State, y = Count, fill = Status)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "Status of Projects by States", x = "State", y = "Count") +
  theme_bw() +
  facet_wrap(~ Status, nrow = 1) +
  theme(axis.text.x = element_text(angle = 78, hjust = 1))


```


Business cycles. Does the expenditure tend to vary with the level of economic activity or are they independent of cycles?

```{r}
# Create a bar plot of project costs (economic activity) by state
ggplot(data, aes(x = State, y = `Total Project Costs...13`)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Project Costs by States Economic Activity", x = "State", y = "Project Costs") +
  theme_bw()+ theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())

```


Trends. Are locations or project types affecting expenditure tend?

```{r}
library(ggplot2)

ggplot(data, aes(x = State, y = `Total Project Costs...13`, color = `Project Type`)) +
  geom_point() +
  labs(x = "State", y = "Total Project Costs", title = "Relationship between State and Total Project Costs") +
  theme_bw()

```

Outliers and historical anomalies. Does the data contain any extreme values that need to be explained? It could be that these represent highly anomalous events that don't add to the predictive power of the data set.

```{r}

# Numeric columns to analyze
numeric_columns <- names(data)[sapply(data, is.numeric)]


# Visualize data using box plots
boxplot_data <- data[, numeric_columns]
boxplot(boxplot_data, main = "Boxplot of Numeric Variables")

# Calculate z-scores for all numerical variables
z_scores <- scale(data[, sapply(data, is.numeric)])

# Identify outliers using z-scores
z_scores <- as.data.frame(scale(data[, numeric_columns]))
outliers <- which(abs(z_scores) > 3)
num_outliers <- length(outliers)  # Count of outliers
print(paste("Number of outliers:", num_outliers))

```

Relationships between variables. Are there important relationships between variables that could aid in forecasting?
Based on your exploratory analysis and understanding of the data, you identify and propose potential methods (regression, time series forecasting, machine learning, etc.) to provide solutions to the business problem.


```{r}

# Perform regression analysis
lm_model <- lm(Complete ~ `Project Type` + `Total Project Costs...13`, data = data)
summary(lm_model)

```

# How does Monthly capital spend trend differently by project size, project duration or state

```{r}
library(ggplot2)

# Subset the relevant columns from the data
subset_data <- data[, c("Total Project Costs...13", "Project Type", "State")]

# Remove rows with missing values in Total Project Costs...13
subset_data <- subset_data[!is.na(subset_data$`Total Project Costs...13`), ]

# Create a box plot to compare Total Project Costs by Project Type
ggplot(subset_data, aes(x = `Project Type`, y = `Total Project Costs...13`)) +
  geom_boxplot() +
  labs(x = "Project Type", y = "Total Project Costs",
       title = "Comparison of Total Project Costs by Project Type") +
  theme_bw()

# Create a bar plot to compare Total Project Costs by State
ggplot(subset_data, aes(x = `State`, y = `Total Project Costs...13`, fill = `State`)) +
  geom_bar(stat = "identity") +
  labs(x = "State", y = "Total Project Costs",
       title = "Comparison of Total Project Costs by State") +
  theme_bw()+
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())

```



