---
title: "speedDating"
date: "2023-04-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=FALSE, warning=FALSE}
library(readr)
data <- read_csv("C:/Users/Admins/Pictures/Camera Roll/speedDating.csv")
names(data)
```


# Assessment of the data and Descriptive statistics

```{r}
# Check for missing values
sum(is.na(data))
summary(data)

```



```{r}
table(data$sex)
```


```{r}
cor_table <- cor(data[c("age", "rc")])
cat("Correlation Table for: Age and RC\n")
print(cor_table, 
      row.names = c("Age", "RC"), 
      col.names = c("Age", "RC"), 
      digits = 4)

```

Principal component analysis (PCA) which is part of the Exploratory Data Analysis(EDA)

```{r}

# Perform PCA on age and rc columns
pca <- prcomp(data[, c("age", "rc")], scale = TRUE)

# View the results
summary(pca)

```
Linear regression model table

```{r}
# Run a linear regression model for rc using age and sex as predictors
model <- lm(rc ~ age + sex, data = data)

# Create a summary table for the model coefficients
coef_table <- summary(model)$coefficients
coef_table
```


```{r}
model <- lm(rc ~ sex + rotate, data = data)
summary(model)

```

ANOVA(analysis of variance) table

```{r}
# Analysis of variance of rc on rotate
model <- aov(rc ~ rotate, data = data)
summary(model)

```

Graphical tools to explore the relationship between variables

1. Relationship between Response by Gender


```{r, message=FALSE, warning=FALSE}
# Scatter plot of age by response
ggplot(data, aes(x = age, y = rc)) +
  geom_jitter(aes(color = sex), alpha = 0.5) +
  scale_color_manual(values = c("#1F78B4", "#E31A1C")) +
  xlim(18, 60) +
  theme_bw()+
  labs(title = "Relationship between Response by Gender")

```
2. Relationship between Age and Rating Count by Gender

```{r}
# Create a boxplot
ggplot(data, aes(x = sex, y = rc, fill = sex)) +
  geom_boxplot() +
  labs(x = "Gender", y = "Rating Count", title = "Relationship between Age and Rating Count by Gender")

```
3. Distribution of Age by Gender

```{r}
ggplot(data, aes(x = age, fill = sex)) +
  geom_histogram(binwidth = 2, alpha = 0.5) +
  facet_wrap(~ sex, ncol = 2) +
  labs(x = "Age", y = "Count", title = "Distribution of Age by Gender")+ theme_bw()

```
4. Density plot of age by sex

```{r}
# Density plot of age by sex
ggplot(data, aes(x = age, fill = sex)) +
  geom_density(alpha = 0.5) +
  xlim(18, 60) +
  theme_bw()+
  labs(title = "Density plot of age by sex")
```
Plot of sex frequency 

```{r}
library(ggplot2)

# Create a bar plot of sex frequency
ggplot(data, aes(x = sex, fill = sex)) +
  geom_bar() +
  scale_fill_manual(values = c("blue", "pink")) +
  xlab("Sex") +
  ylab("Frequency") +
  ggtitle("Frequency of Males and Females")

```


```{r}
# Create a bar plot of rotation frequency by sex
ggplot(data, aes(x = sex, fill = rotate)) +
  geom_bar(position = "stack") +
  scale_fill_manual(values = c("blue", "pink")) +
  xlab("Sex") +
  ylab("Frequency") +
  ggtitle("Frequency of Rotation by Sex")

```


```{r}
table(data$sex)
table(data$rotate)
summary(data$age)
mean_age = mean(data$age);mean_age# the average age is 19years
```

frquency distribution using histgoram for rating

```{r}
# frquency distribution using histgoram for rating
ggplot(data, aes(x=rc))+
  geom_area(aes(y=..count..), bins = 30, stat = 'bin', fill='steelblue')+
theme_bw()+
  labs(title = "Frequency distribution for the average romantic chemistry rating of respondents")
```


```{r}
# Aggregate rc column by sex
rc_by_sex <- aggregate(rc ~ sex, data = data, FUN = sum)

# View aggregated data
rc_by_sex

```


```{r}
#section 2
# effect size calculations
n = nrow(data);n
dataa = data.frame(data)
male =dataa[dataa$sex == "m",]
sum(male$rc)
female =dataa[dataa$sex == "f",]
sum(female$rc)
n_s = nrow(male)
female = dataa[dataa$sex == "f", ]
mean_male = mean(male$rc);mean_male
mean_female = mean(female$rc); mean_female
variance_male = var(male$rc)
variance_female = var(female$rc)
effect = mean_male-mean_female; effect
n1 = nrow(male)-1
n2 = nrow(female)-1
N = n1+n2-2
x = n1*variance_male
y = n2*variance_female
effectSE = sqrt((x+y)/N)
effectsize = effect/effectSE; effectsize
#CI
df = n-1
w <- effectSE * qt(0.975, df)
effect-w
effect+w

effectM = sum(var(male$rc));effectM
effectSE_M = sqrt( effectM / n_s)

effectF = sum(var(female$rc));effectF
effectSE_F = sqrt( effectF / n_s)

wC <- effectSE_M * qt(0.975, df)
wA <- effectSE_F * qt(0.975, df)
wC; wA
# CIs
effectM - wC ; effectM + wC
effectF - wA ; effectF + wA

#CI

s <- data.frame( sex = c('m', 'f'),
                 eff = c(effectM, effectF),
                 lo = c(effectM - wC, effectF - wA),
                 hi = c(effectM + wC, effectF + wA))
s$sex <- factor(s$sex, level = c('m', 'f'))
```


